Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2021-10-10 proposalPres.tex
Updated presentation slides, system level requirement document, lab notebook, and figures folder

\title[HIL Plant Modeling]{Hardware-in-Loop Plant Modeling for Autonomous
  Vehicle}

@@

\author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman 
\linebreak Advisors:~Dr.~Suruz~Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\begin{frame}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{large}
      Model vehicle subsystems for a Lexus platform.
 \begin{itemize}
          \item Steering Model
          \item Acceleration Model
          \item Brake Model
          \item Shift Model
          \item Speed Model
          \item Speed Control Model
        \end{itemize} 
    \end{large}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{large}
      Use conventional System Identification techniques for modeling subsystems based on available raw data.  
    \end{large}
  \end{block}
\end{frame}

@@

\begin{frame}{Literature Review}
  \begin{block}{Existing Solution}
        Use of System Identification Toolbox in Matlab to create models from data~\cite{Donjaroennon2021}
  \end{block}
  \begin{block}{Existing Solution}
        Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
  \end{block}
  \begin{block}{Existing Solution}
        Steer-By-Wire method as a system model~\cite{Saruchi2015}
  \end{block}
    % \begin{figure}[b]
    %     \centering
    %     \includegraphics[width=0.45\textwidth]{figs/img/CompaRob}
    %     \caption{CompaRob}
    %     %\label{fig:sysBlockDiag}
    % \end{figure}
\end{frame}

@@

\begin{frame}{Existing Solutions}
  \begin{block}{Problems}
    \begin{itemize}
      \item Require line-of-sight between robot and user
      \item Some require costly dedicated image processing hardware
    \end{itemize}
  \end{block}
  \pause
  \begin{block}{Benefits of Proposed Solution}
    \begin{itemize}
      \item High level of accuracy 
    \end{itemize}
  \end{block}
\end{frame}

@@

\section{System Requirements}
\begin{frame}{System Requirements}
  \begin{block}{Specifications}
    \begin{itemize}
      	\item The plant model should have an accurate model of the six main subsystems
    		\item A hardware-in-loop (HIL) test bench can be developed from the plant models of the subsystems
    		\item The steering model can handle very small steering angles
    \end{itemize}
  \end{block}
\end{frame}

>>>>

\title[HIL Plant Modeling]{Hardware-in-the-Loop Plant Modeling for Autonomous
  Vehicle}

@@

\author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman 
\linebreak Advisor:~Dr.~Suruz~Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\begin{frame}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{large}
      Model vehicle subsystems for a Lexus platform.
 \begin{itemize}
          \item Steering Model
          \item Acceleration Model
          \item Brake Model
          \item Shift Model
          \item Speed Model
          \item Speed Control Model
        \end{itemize} 
    \end{large}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{large}
      A potential solution is to develop conventional System Identification techniques for modeling subsystems using available raw data.  
    \end{large}
  \end{block}
\end{frame}

@@

\begin{frame}{Literature Review}
  \begin{block}{Existing Solution}
 \begin{itemize}
        \item Use of System Identification Toolbox in Matlab to create models from data~\cite{Adnan2010}
	 \begin{itemize}
		    \tiny
		    		\item Offers a variety of model choices
				\item Needs a large amount of raw data to produce an accurate model
	\end{itemize}
	\item Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
	 \begin{itemize}
		    \tiny
		    		\item Allows the use of traditional analysis methods to create a model 
				\item More room for error during calculations
	\end{itemize}
	\item Steer-By-Wire method as a system model~\cite{Saruchi2015}
	 \begin{itemize}
		    \tiny
		    		\item Can model systems with small non-linearities 
				\item Mechanical components replaced by electrical components 
	\end{itemize}
\end{itemize}
  \end{block}
    % \begin{figure}[b]
    %     \centering
    %     \includegraphics[width=0.45\textwidth]{figs/img/CompaRob}
    %     \caption{CompaRob}
    %     %\label{fig:sysBlockDiag}
    % \end{figure}
\end{frame}

@@

%\begin{frame}{Existing Solutions}
%  \begin{block}{Problems}
%    \begin{itemize}
%      \item Require line-of-sight between robot and user
%      \item Some require costly dedicated image processing hardware
%    \end{itemize}
%  \end{block}
%  \pause
%  \begin{block}{Benefits of Proposed Solution}
%    \begin{itemize}
%      \item High level of accuracy 
%    \end{itemize}
%  \end{block}
%\end{frame}

@@

\section{System Requirements}
\begin{frame}
\tiny
	\begin{block}{System Inputs and Outputs}
		\begin{itemize}
			\tiny
		    \item Steering Model
		    \begin{itemize}
		    \tiny
		    		\item Torque Voltages
		    		\begin{itemize}
		    		\tiny
		    			\item Desired Steering Wheel Angle
		    			\item Actual Steering Wheel Angle
		    		\end{itemize}
		    \end{itemize}
		    \item Acceleration Model
		    \begin{itemize}
		    \tiny
		    		\item Acceleration Pedal Voltages
		    \end{itemize}
		    \item Brake Model
		    \begin{itemize}
		    \tiny
		    		\item Brake Pedal Pressure Voltages
		    		\item Brake Pedal Stroke Voltages 
		    		\item Brake Pedal On/Off Switch
		    \end{itemize}
		    \item Shift Model
		    \begin{itemize}
		    \tiny
		    		\item Desired Shift Gear
		    \end{itemize}
		    \item Speed Model
		    \begin{itemize}
		    \tiny
		    		\item Acceleration Pedal Position
		    		\item Brake Pedal Position
		    		\item Shifter Actual Gear
		    \end{itemize}
		    \item Speed Control Model
		    \begin{itemize}
		    \tiny
		    		\item Desired Vehicle Speed
		    \end{itemize}
		\end{itemize}
	\end{block}
\end{frame}
\begin{frame}			
	\begin{figure}
		\includegraphics[width=10cm]{figs/inkscape/steeringModelArchitecture}
		\caption{Block Diagram of Steering Subsystem}
		\label{fig:steeringModel}
	\end{figure}
\end{frame}

\begin{frame}{System Requirements}
  \begin{block}{Specifications}
    \begin{itemize}
      	\item The plant model should have an accurate model of the six main subsystems
    		\item A hardware-in-loop (HIL) test bench can be developed from the plant models of the subsystems
    		\item The steering model can handle very small steering angles
    \end{itemize}
  \end{block}
\end{frame}

### 2021-10-10 systemLevelFunctionalRequirements.tex
Updated presentation slides, system level requirement document, lab notebook, and figures folder

\usepackage{hyperref}
\usepackage{todonotes}

@@

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

@@

\title{
    \begin{center}
        \href{http://www.bradley.edu}{\includegraphics[height=1in]{figs/logoBU1-Print}}
        \vskip10pt
        \HRule \\[0.4cm]
        {\Huge \bfseries HIL Plant Modeling \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
        \HRule \\[0.4cm]
    \end{center}
    }
\author{Hannah Grady and Nicholas Nauman \\ \underline{Advisors}: Dr. Suruz Miah}

@@

\section{Project Description}
Autonomous vehicles are being developed by many companies for commercial and personal use. These autonomous vehicles would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers. Also, autonomous vehicles have the ability to make roads safer for drivers and pedestrians alike. To control autonomous vehicles, accurate models of six main vehicle subsystems must be created so controllers can be developed to reliably manage the system.

@@

Researchers in ~\cite{Adnan2010} show how a system with small non-linearities can be modeled using Matlab's System Identification Toolbox. Since the researchers were able to model their system successfully, that indicates that we should be able to model our steering model with its small non-linearities caused by very small steering angles as well. Another method for modeling small non-linearities is introduced by the authors in ~\cite{Saruchi2015} using a Steer-By-Wire method as the model for the steering system. With this model a composite nonlinear feedback (CNF) PID controller can be implemented to control the steering system even for small turning angles. Another option for modeling the steering system is using a third order ARMAX model as proposed by ~\cite{Li1999}. Using this model, traditional analysis methods can be used to develop a model and controller. Any concerns that modeling the vehicle components using the System Identification Toolbox will produce inaccurate results are addressed by ~\cite{Donjaroennon2021}. Using input and output signals, they were able to come up with a model that had a best fit percentage of 95.1\%. With these options for modeling automotive systems, we can carry out our project knowing that the models we produce will be accurate.

%------------------------------------------------
\section{System Architecture}
\subsection{System Block Diagram}
The Lexus car platform is comprised of six main subsystems - a steering model, an acceleration model, a brake model, a shifting model, a speed model, and a cruise model. The system, as a whole, will be taking into consideration obstacles around it while the vehicle traverses a predetermined route. For the system to be able to accomplish this reliably, the six main subsystems must be precisely modeled, especially the steering subsystem. A block diagram of the vehicle steering model is shown in \autoref{fig:sysBlockDiag}
\begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=3.5in]{figs/inkscape/steeringModelArchitecture}
    \caption{Block Diagram of the Vehicle Steering Model}
    \label{fig:sysBlockDiag}
\end{figure}

@@

\begin{itemize}
    \item Steering Model
    \begin{itemize}
    		\item Torque Voltages
    		\begin{itemize}
    			\item Desired Steering Wheel Angle
    			\item Actual Steering Wheel Angle
    		\end{itemize}
    \end{itemize}
    \item Acceleration Model
    \begin{itemize}
    		\item Acceleration Pedal Voltages
    \end{itemize}
    \item Brake Model
    \begin{itemize}
    		\item Brake Pedal Pressure Voltages
    		\item Brake Pedal Stroke Voltages 
    		\item Brake Pedal On/Off Switch
    \end{itemize}
    \item Shift Model
    \begin{itemize}
    		\item Desired Shift Gear
    \end{itemize}
    \item Speed Model
    \begin{itemize}
    		\item Acceleration Pedal Position
    		\item Brake Pedal Position
    		\item Shifter Actual Gear
    \end{itemize}
    \item Speed Control Model
    \begin{itemize}
    		\item Desired Vehicle Speed
    \end{itemize}
\end{itemize}

>>>>

\usepackage{hyperref}

% \usepackage{easyReview}

@@

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents

\usepackage[colorinlistoftodos]{todonotes}
\usepackage{soul}

\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

@@

\title{
    \begin{center}
        \href{http://www.bradley.edu}{\includegraphics[height=1in]{figs/logoBU1-Print}}
        \vskip10pt
        \HRule \\[0.4cm]
        {\Huge \bfseries Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
        \HRule \\[0.4cm]
    \end{center}
    }
\author{Hannah Grady and Nicholas Nauman \\ \underline{Advisor}: Dr. Suruz Miah}

@@

\section{Project Description}
Autonomous vehicles are being developed by many companies for commercial and/or personal use. These autonomous vehicles would allow companies to continue crucial deliveries or transports of their products even if there is a shortage of drivers. Also, autonomous vehicles have the ability to make roads safer for drivers and pedestrians alike. To control autonomous vehicles, accurate models of six main vehicle subsystems must be created so controllers can be developed to reliably manage the system.

@@

Researchers in~\cite{Adnan2010} show how a system with small non-linearities can
be modeled using Matlab's System Identification Toolbox. Since the researchers
were able to model their system successfully, that indicates that we should be
able to model our steering model with its small non-linearities caused by very
small steering angles as well. Another method for modeling small non-linearities
is introduced by the authors in~\cite{Saruchi2015} using a Steer-By-Wire method
as the model for the steering system. With this model, a composite nonlinear
feedback (CNF) PID controller can be implemented to control the steering system
even for small turning angles. Another option for modeling the steering system
is using a third order ARMAX model as proposed by~\cite{Li1999}. Using this
model, traditional analysis methods can be used to develop a model and
controller. Any concerns that modeling the vehicle components using the System
Identification Toolbox will produce inaccurate results are addressed by
~\cite{Donjaroennon2021}. Using input and output signals, they were able to come
up with a model that had a best fit percentage of 95.1\%. With these options for
modeling automotive systems, we can carry out our project knowing that the
models we produce will be accurate.

%------------------------------------------------
\section{System Architecture}
\subsection{System Block Diagram}
The Lexus car platform is comprised of six main subsystems - a steering model,
an acceleration model, a brake model, a shifting model, a speed model, and a
cruise model. The system, as a whole, will be taking into consideration
obstacles around it while the vehicle traverses a predetermined route. For the
system to be able to accomplish this reliably, the six main subsystems must be
precisely modeled, especially the steering subsystem. A block diagram of the
vehicle steering model is shown in \autoref{fig:sysBlockDiag}. %
%
\begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=3.5in]{figs/inkscape/steeringModelArchitecture}
    \caption{Block Diagram of the Vehicle Steering Model.}
    \label{fig:sysBlockDiag}
\end{figure}
%

@@

\todo[inline]{For the steering model, is it a single input (torque voltage) and multiple output system?}
\begin{itemize}
    \item Steering Model
    \begin{itemize}
    		\item Torque Voltages
    		\begin{itemize}
    			\item Desired Steering Wheel Angle
    			\item Actual Steering Wheel Angle
    		\end{itemize}
    \end{itemize}
    \item Acceleration Model
    \begin{itemize}
    		\item Acceleration Pedal Voltages
    \end{itemize}
    \item Brake Model
    \begin{itemize}
    		\item Brake Pedal Pressure Voltages
    		\item Brake Pedal Stroke Voltages 
    		\item Brake Pedal On/Off Switch
    \end{itemize}
    \item Shift Model
    \begin{itemize}
    		\item Desired Shift Gear
    \end{itemize}
    \item Speed Model
    \begin{itemize}
    		\item Acceleration Pedal Position
    		\item Brake Pedal Position
    		\item Shifter Actual Gear
    \end{itemize}
    \item Speed Control Model
    \begin{itemize}
    		\item Desired Vehicle Speed
    \end{itemize}
\end{itemize}
